### 2023-01-24 article.tex
Remove all usages of `'ll`, except in the last sentence

This paper is about paradata in the context of a computational
experiment in general and uses an example from genetic 
epidemiology in particular.
We'll postpone the introduction to genetic epidemiology now
and focus on 'computational experiment' first.
A computational experiment is an experiment run by computer code.
In chronologic order, it usually collects primary data first, 
then runs an analysis, which finally results in the generation of results.

@@

The (scientific) article is metadata, as it is data that describes other data:
an article describes the
experiment; an article describes what the code does in a natural 
language, such as English (which I'll use from now on).
However, English (or any other natural language) is not the best
candidate to describe how the data is collected,
as it only has a loose connection with collecting the data.
If the code and article of an experiment disagree,
it is the code that actually let the data be collected.  
Instead, an article is metadata about a research.

>>>>

This paper is about paradata in the context of a computational
experiment in general and uses an example from genetic 
epidemiology in particular.
The introduction to genetic epidemiology will be postponed for now,
insteaf focussing on 'computational experiment' first.
A computational experiment is an experiment run by computer code.
In chronologic order, it usually collects primary data first, 
then runs an analysis, which finally results in the generation of results.

@@

The (scientific) article is metadata, as it is data that describes other data:
an article describes the
experiment; an article describes what the code does in a natural 
language, such as English.
However, English (or any other natural language) is not the best
candidate to describe how the data is collected,
as it only has a loose connection with collecting the data.
If the code and article of an experiment disagree,
it is the code that actually let the data be collected.  
Instead, an article is metadata about a research.
